SAT Competition 2020\tnoteref{title}

### 2021-01-28 paper/main.tex
more on results

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
\end{figure}

@@

\subsubsection{Kissat}

>>>>

Some interesting results were observed in the 2020 SAT Competition.
Four Main track solvers (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
performed significantly better compared to the others, see Figure~\ref{main:all} and Table~\ref{tab:results}.
These four top solvers all have a different code base, which is rare. In recent competitions, top solvers were much closer together.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
Since the SAT Competition started to rank based on PAR-2 score, such cases have been observed several times.

The main reason for the separation between the top four solvers and the others is the enormous gap on satisfiable benchmarks, 
see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
their performance on satisfiable instance. Examples of such techniques are the integration of a local search
solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts,
and variable-move-to-front). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by 
\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.

The solver performances on unsatisfiable formulas was much closer,
see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
performed significantly better compared to all other participants. It is therefore not surprising
that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver,
which has been implemented in C, while most solvers are implemented in C++. Further 
details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
The solvers \solver{CaDiCaL-trial}
and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
\label{main:all}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
\label{main:sat}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
\end{figure}
\label{main:unsat}

@@

\subsubsection{Kissat} 
\label{sec:kissat}
